---
title: "Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r results='hide', echo=FALSE, include=FALSE}
# this should all be functional, it sucks
suppressMessages({
  library(sjstats)
  library(tidyverse)
  library(readxl)
  library(lsr)
  source("supplemental_generation.R")
})
```

```{r, echo=FALSE, results='hide', include=FALSE}
# Fear
#########################
fearAnovaData <- allSupplemental %>% 
  dplyr::filter(Experiment == "fear")
fearDprimeAnova <- summary(
  aov(
    dPrime ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = fearAnovaData
  )
)
fearDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = fearAnovaData
  )
)
fearCriterionAnova <- summary(
  aov(
    Criterion ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = fearAnovaData
  )
)
fearCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = fearAnovaData
  )
)

# Noise
#########################
noiseAnovaData <- allSupplemental %>% 
  dplyr::filter(Experiment == "noise")
noiseDprimeAnova <- summary(
  aov(
    dPrime ~ Noise * GroupSize + Error(ParticipantNumber / (Noise * GroupSize)),
    data = noiseAnovaData
  )
)
noiseCriterionAnova <- summary(
  aov(
    Criterion ~ Noise * GroupSize + Error(ParticipantNumber / (Noise * GroupSize)),
    data = noiseAnovaData
  )
)
noiseDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ Noise * GroupSize + Error(ParticipantNumber / (Noise * GroupSize)),
    data = noiseAnovaData
  )
)
noiseCriterionEtaSq<-sjstats::anova_stats(
  aov(
    Criterion ~ Noise * GroupSize + Error(ParticipantNumber / (Noise * GroupSize)),
    data = noiseAnovaData
  )
)

# Group Size Intensity Collapsed
#########################
groupSizeIntensityCollapsedAnovaData <- allSupplemental %>% 
  dplyr::filter(Experiment == "group_size_intensity_collapsed")
groupSizeIntensityCollapsedDprimeAnova <- summary(
  aov(
    dPrime ~ GroupSize + Error(ParticipantNumber / GroupSize),
    data = groupSizeIntensityCollapsedAnovaData
  )
)
groupSizeIntensityCollapsedCriterionAnova <- summary(
  aov(
    Criterion ~ GroupSize + Error(ParticipantNumber / GroupSize),
    data = groupSizeIntensityCollapsedAnovaData
  )
)
groupSizeIntensityCollapsedDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ GroupSize + Error(ParticipantNumber / GroupSize),
    data = groupSizeIntensityCollapsedAnovaData
  )
)
groupSizeIntensityCollapsedCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ GroupSize + Error(ParticipantNumber / GroupSize),
    data = groupSizeIntensityCollapsedAnovaData
  )
)

# Group Size Group Collapsed
#########################
groupSizeIGroupCollapsedAnovaData <- allSupplemental %>% 
  dplyr::filter(Experiment == "group_size_group_collapsed")
groupSizeGroupCollapsedDprimeAnova <- summary(
  aov(
    dPrime ~ Intensity + Error(ParticipantNumber / Intensity),
    data = groupSizeIGroupCollapsedAnovaData
  )
)
groupSizeGroupCollapsedCriterionAnova <- summary(
  aov(
    Criterion ~ Intensity + Error(ParticipantNumber / Intensity),
    data = groupSizeIGroupCollapsedAnovaData
  )
)
groupSizeGroupCollapsedDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ Intensity + Error(ParticipantNumber / Intensity),
    data = groupSizeIGroupCollapsedAnovaData
  )
)
groupSizeGroupCollapsedCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ Intensity + Error(ParticipantNumber / Intensity),
    data = groupSizeIGroupCollapsedAnovaData
  )
)

# Identity
#########################
identityAnovaData <- allSupplemental %>% 
  dplyr::filter(Experiment == "identity")
identityDprimeAnova <- summary(
  aov(
    dPrime ~ Intensity * IdentityCondition + Error(ParticipantNumber / (Intensity * IdentityCondition)),
    data = identityAnovaData
  )
)
identityCriterionAnova <- summary(
  aov(
    Criterion ~ Intensity * IdentityCondition + Error(ParticipantNumber / (Intensity * IdentityCondition)),
    data = identityAnovaData
  )
)
identityDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ Intensity * IdentityCondition + Error(ParticipantNumber / (Intensity * IdentityCondition)),
    data = identityAnovaData
  )
)
identityCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ Intensity * IdentityCondition + Error(ParticipantNumber / (Intensity * IdentityCondition)),
    data = identityAnovaData
  )
)

# Gender
#########################
genderAnovaData <- allSupplemental %>% 
  dplyr::filter(Experiment == "gender_crowd_type")
genderDprimeAnova <- summary(
  aov(
    dPrime ~ IntensityType * GroupType + Error(ParticipantNumber / (IntensityType * GroupType)),
    data = genderAnovaData
  )
)
genderCriterionAnova <- summary(
  aov(
    Criterion ~ IntensityType * GroupType + Error(ParticipantNumber / (IntensityType * GroupType)),
    data = genderAnovaData
  )
)
genderDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ IntensityType * GroupType + Error(ParticipantNumber / (IntensityType * GroupType)),
    data = genderAnovaData
  )
)
genderCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ IntensityType * GroupType + Error(ParticipantNumber / (IntensityType * GroupType)),
    data = genderAnovaData
  )
)
# Gender Group Size
#########################
genderGroupSizeAnovaData <- allSupplemental %>% 
  dplyr::filter(
    Experiment == "gender", 
    Gender != 3
  )
genderGroupSizeDprimeAnova <- summary(
  aov(
    dPrime ~ Intensity * Gender * GroupSize + Error(ParticipantNumber / (Intensity * Gender * GroupSize)),
    data = genderGroupSizeAnovaData
  )
)
genderGroupSizeCriterionAnova <- summary(
  aov(
    Criterion ~ Intensity * Gender * GroupSize + Error(ParticipantNumber / (Intensity * Gender * GroupSize)),
    data = genderGroupSizeAnovaData
  )
)
genderGroupSizeDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ Intensity * Gender * GroupSize + Error(ParticipantNumber / (Intensity * Gender * GroupSize)),
    data = genderGroupSizeAnovaData
  )
)
genderGroupSizeCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ Intensity * Gender * GroupSize + Error(ParticipantNumber / (Intensity * Gender * GroupSize)),
    data = genderGroupSizeAnovaData
  )
)

# Crowd Vs Single
#########################
crowdSingleAnovaData <- allSupplemental %>%
  dplyr::filter(Experiment == "crowdVsSingle")
crowdSingleDprimeAnova <- summary(
  aov(
    dPrime ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = crowdSingleAnovaData
  )
)
crowdSingleCriterionAnova <- summary(
  aov(
    Criterion ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = crowdSingleAnovaData
  )
)
crowdSingleDprimeEtaSq <- sjstats::anova_stats(
  aov(
    dPrime ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = crowdSingleAnovaData
  )
)
crowdSingleCriterionEtaSq <- sjstats::anova_stats(
  aov(
    Criterion ~ Intensity * GroupSize + Error(ParticipantNumber / (Intensity * GroupSize)),
    data = crowdSingleAnovaData
  )
)
```

## Crowd Vs. Single
### dPrime ANOVA
```{r echo=FALSE}
crowdSingleDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
crowdSingleCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
crowdSingleDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
crowdSingleCriterionEtaSq
```

### T-Tests & Cohen's Ds
```{r echo=FALSE}
groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(Experiment == "crowdVsSingle") %>% 
  dplyr::group_by(ParticipantNumber, GroupSize) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

single <- groupSizeGrouped %>% 
  dplyr::filter(GroupSize == 1)

crowd <- groupSizeGrouped %>% 
  dplyr::filter(GroupSize == 12)

singleCohenDPrime<- lsr::cohensD(single$meanDprime)
singleTtestDPrime <- t.test(single$meanDprime)
singleCohenCriterion<- lsr::cohensD(single$meanCriterion)
singleTtestCriterion <- t.test(single$meanCriterion)

crowdCohenDPrime<- lsr::cohensD(crowd$meanDprime)
crowdTtestDPrime <- t.test(crowd$meanDprime)
crowdCohenCriterion<- lsr::cohensD(crowd$meanCriterion)
crowdTtestcriterion <- t.test(crowd$meanCriterion)  

corrData <- cbind(single, crowd) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(meanCriterion, meanCriterion1, meanDprime, meanDprime1) %>% 
  dplyr::rename(
    singleC = meanCriterion, 
    crowdC = meanCriterion1, 
    singleD = meanDprime,
    crowdD = meanDprime1
  ) %>% 
  dplyr::mutate(
    DprimeDiff = crowdD - singleD, 
    CriterionDiff = crowdC - singleC
  )

criterionLinearMod <- lm(singleC ~ crowdC, data = corrData)
criterionRsquared <- summary(criterionLinearMod)$r.squared

singleTtestcriterion
singleCohenCriterion
singleTtestDPrime
singleCohenDPrime

crowdTtestcriterion
crowdCohenDPrime
crowdTtestDPrime
crowdCohenDPrime
```

### R Squared
```{r, echo=FALSE}
criterionRsquared
```

## Fear
### dPrime ANOVA
```{r echo=FALSE}
fearDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
fearCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
fearDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
fearCriterionEtaSq
```

### T Tests & Cohen's D
```{r echo=FALSE}
groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(Experiment == "fear") %>% 
  dplyr::group_by(ParticipantNumber, GroupSize) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

single <- groupSizeGrouped %>% 
  dplyr::filter(GroupSize == 1)

crowd <- groupSizeGrouped %>% 
  dplyr::filter(GroupSize == 12)

singleCohenDPrime<- lsr::cohensD(single$meanDprime)
singleTtestDPrime <- t.test(single$meanDprime)
singleCohenCriterion<- lsr::cohensD(single$meanCriterion)
singleTtestcriterion <- t.test(single$meanCriterion)

crowdCohenDPrime<- lsr::cohensD(crowd$meanDprime)
crowdTtestDPrime <- t.test(crowd$meanDprime)
crowdCohenCriterion<- lsr::cohensD(crowd$meanCriterion)
crowdTtestcriterion <- t.test(crowd$meanCriterion)  

corrData <- cbind(single, crowd) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(meanCriterion, meanCriterion1, meanDprime, meanDprime1) %>% 
  dplyr::rename(
    singleC = meanCriterion, 
    crowdC = meanCriterion1, 
    singleD = meanDprime,
    crowdD = meanDprime1
  ) %>% 
  dplyr::mutate(
    DprimeDiff = crowdD - singleD, 
    CriterionDiff = crowdC - singleC
  )

criterionLinearMod <- lm(singleC ~ crowdC, data = corrData)
criterionRsquared <- summary(criterionLinearMod)$r.squared

singleTtestcriterion
singleCohenCriterion
singleTtestDPrime
singleCohenDPrime

crowdTtestcriterion
crowdCohenCriterion
crowdTtestDPrime
crowdCohenDPrime
```

### R Squared
```{r}
criterionRsquared
```

### Noise
### dPrime ANOVA
```{r echo=FALSE}
noiseDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
noiseCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
noiseDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
noiseCriterionEtaSq
```

### T Tests & Cohen's D
```{r echo=FALSE}
groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(Experiment == "noise") %>% 
  dplyr::group_by(ParticipantNumber, GroupSize) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

single <- groupSizeGrouped %>% 
  dplyr::filter(GroupSize == 1)

crowd <- groupSizeGrouped %>% 
  dplyr::filter(GroupSize == 12)

singleCohenDPrime<- lsr::cohensD(single$meanDprime)
singleTtestDPrime <- t.test(single$meanDprime)
singleCohenCriterion<- lsr::cohensD(single$meanCriterion)
singleTtestcriterion <- t.test(single$meanCriterion)

crowdCohenDPrime<- lsr::cohensD(crowd$meanDprime)
crowdTtestDPrime <- t.test(crowd$meanDprime)
crowdCohenCriterion<- lsr::cohensD(crowd$meanCriterion)
crowdTtestcriterion <- t.test(crowd$meanCriterion)  

corrData <- cbind(single, crowd) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(meanCriterion, meanCriterion1, meanDprime, meanDprime1) %>% 
  dplyr::rename(
    singleC = meanCriterion, 
    crowdC = meanCriterion1, 
    singleD = meanDprime,
    crowdD = meanDprime1
  ) %>% 
  dplyr::mutate(
    DprimeDiff = crowdD - singleD, 
    CriterionDiff = crowdC - singleC
  )

criterionLinearMod <- lm(singleC ~ crowdC, data = corrData)
criterionRsquared <- summary(criterionLinearMod)$r.squared

singleTtestcriterion
singleCohenCriterion
singleTtestDPrime
singleCohenDPrime

crowdTtestcriterion
crowdCohenCriterion
crowdTtestDPrime
crowdCohenDPrime
```

### R Squared
```{r}
criterionRsquared
```

## Crowd Size (Intensity Collapsed)
### dPrime ANOVA
```{r echo=FALSE}
groupSizeIntensityCollapsedDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
groupSizeIntensityCollapsedCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
groupSizeIntensityCollapsedDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
groupSizeIntensityCollapsedCriterionEtaSq
```

## Crowd Size (Group Collapsed)
### dPrime ANOVA
```{r echo=FALSE}
groupSizeGroupCollapsedDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
groupSizeGroupCollapsedCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
groupSizeGroupCollapsedDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
groupSizeGroupCollapsedCriterionEtaSq
```

## Identity
### dPrime ANOVA
```{r echo=FALSE}
identityDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
identityCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
identityDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
identityCriterionEtaSq
```

### T Tests & Cohen's D
```{r echo=FALSE}
groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(
    Experiment == "identity",
    IdentityCondition != 1
  ) %>%
  dplyr::group_by(ParticipantNumber, Intensity, IdentityCondition) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

intensity1 <- groupSizeGrouped %>% dplyr::filter(Intensity == 1)
intensity10 <- groupSizeGrouped %>% dplyr::filter(Intensity == 10)
intensity20 <- groupSizeGrouped %>% dplyr::filter(Intensity == 20)
intensity30 <- groupSizeGrouped %>% dplyr::filter(Intensity == 30)
intensity40 <- groupSizeGrouped %>% dplyr::filter(Intensity == 40)
intensity50 <- groupSizeGrouped %>% dplyr::filter(Intensity == 50)

intensity1DPrimeTtest <- t.test(
  meanDprime ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity1
)
intensity10DPrimeTtest <- t.test(
  meanDprime ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity10
)
intensity20DPrimeTtest <- t.test(
  meanDprime ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity20
)
intensity30DPrimeTtest <- t.test(
  meanDprime ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity30
)
intensity40DPrimeTtest <- t.test(
  meanDprime ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity40
)
intensity50DPrimeTtest <- t.test(
  meanDprime ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity50
)

intensity1CriterionTtest <- t.test(
  meanCriterion ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity1
)
intensity10CriterionTtest <- t.test(
  meanCriterion ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity10
)
intensity20CriterionTtest <- t.test(
  meanCriterion ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity20
)
intensity30CriterionTtest <- t.test(
  meanCriterion ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity30
)
intensity40CriterionTtest <- t.test(
  meanCriterion ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity40
)
intensity50CriterionTtest <- t.test(
  meanCriterion ~ IdentityCondition, 
  paired = TRUE, 
  data = intensity50
)

groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(
    Experiment == "identity"
  ) %>%
  dplyr::group_by(ParticipantNumber, IdentityCondition) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

single <- groupSizeGrouped %>% 
  dplyr::filter(IdentityCondition == 1)

homogeneousCrowd <- groupSizeGrouped %>% 
  dplyr::filter(IdentityCondition == 2)

heterogeneousCrowd <- groupSizeGrouped %>% 
  dplyr::filter(IdentityCondition == 3)

singleCohenDPrime<- lsr::cohensD(single$meanDprime)
singleTtestDPrime <- t.test(single$meanDprime)
singleCohenCriterion<- lsr::cohensD(single$meanCriterion)
singleTtestcriterion <- t.test(single$meanCriterion)

heterogeneousCrowdCohenDPrime<- lsr::cohensD(heterogeneousCrowd$meanDprime)
heterogeneousCrowdTtestDPrime <- t.test(heterogeneousCrowd$meanDprime)
heterogeneousCrowdCohenCriterion<- lsr::cohensD(heterogeneousCrowd$meanCriterion)
heterogeneousCrowdTtestcriterion <- t.test(heterogeneousCrowd$meanCriterion)  

homogeneousCrowdCohenDPrime<- lsr::cohensD(homogeneousCrowd$meanDprime)
homogeneousCrowdTtestDPrime <- t.test(homogeneousCrowd$meanDprime)
homogeneousCrowdCohenCriterion<- lsr::cohensD(homogeneousCrowd$meanCriterion)
homogeneousCrowdTtestcriterion <- t.test(homogeneousCrowd$meanCriterion)  

singleTtestcriterion
singleCohenCriterion
singleTtestDPrime
singleCohenDPrime

crowdTtestcriterion
crowdCohenCriterion
crowdTtestDPrime
crowdCohenDPrime
```

## Gender By Group Size (No Mixed Group)
### dPrime ANOVA
```{r echo=FALSE}
genderGroupSizeDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
genderGroupSizeCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
genderGroupSizeDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
genderGroupSizeCriterionEtaSq
```

### T Tests & Cohen's D
```{r}
groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(
    Experiment == "gender",
    Gender != 3
  ) %>%
  dplyr::group_by(ParticipantNumber, Gender, GroupSize) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

single <- groupSizeGrouped %>% dplyr::filter(GroupSize == 1)
singleMale <- single %>% 
  dplyr::filter(Gender == 1) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull()
singleFemale <- single %>% 
  dplyr::filter(Gender == 2) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull() 

crowd <- groupSizeGrouped %>% filter(GroupSize == 12)
crowdMale <- crowd %>% 
  dplyr::filter(Gender == 1) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull()
crowdFemale <- crowd %>% 
  dplyr::filter(Gender == 2) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull() 

singleTtestCriterion <- t.test(singleMale, singleFemale, paired = TRUE)
singleCohenCriterion <- lsr::cohensD(singleMale, singleFemale)
crowdTtestCriterion <- t.test(meanCriterion ~ Gender, paired = TRUE, data = crowd)
crowdCohenCriterion <- lsr::cohensD(crowdMale, crowdFemale)


groupSizeGrouped <- allSupplemental %>% 
  dplyr::filter(
    Experiment == "gender",
    Gender != 3,
    Intensity %in% c(30, 40, 50)
  ) %>%
  dplyr::group_by(ParticipantNumber, Gender, GroupSize) %>% 
  dplyr::summarise(
    meanDprime = mean(dPrime),
    meanCriterion = mean(Criterion)
  )

single <- groupSizeGrouped %>% dplyr::filter(GroupSize == 1)
singleMale <- single %>% 
  dplyr::filter(Gender == 1) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull()
singleFemale <- single %>% 
  dplyr::filter(Gender == 2) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull() 

crowd <- groupSizeGrouped %>% filter(GroupSize == 12)
crowdMale <- crowd %>% 
  dplyr::filter(Gender == 1) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull()
crowdFemale <- crowd %>% 
  dplyr::filter(Gender == 2) %>% 
  dplyr::ungroup() %>%
  dplyr::select(meanCriterion) %>% 
  dplyr::pull() 

singleFemaleTtestCriterion <- t.test(singleFemale)
singleFemaleCohenCriterion <- lsr::cohensD(singleFemale)
crowdFemaleTTestCriterion <- t.test(crowdFemale)
crowdFemaleCohenCriterion <- lsr::cohensD(crowdFemale)

singleMaleTtestCriterion <- t.test(singleMale)
singleMaleCohenCriterion <- lsr::cohensD(singleMale)
crowdMaleTTestCriterion <- t.test(crowdMale)
crowdMaleCohenCriterion <- lsr::cohensD(crowdMale)
```


## All Gender Combinations & Low-High Intensity Split
### dPrime ANOVA
```{r echo=FALSE}
genderDprimeAnova
```

### Criterion ANOVA
```{r echo=FALSE}
genderCriterionAnova
```

### dPrime eta Squared
```{r echo=FALSE}
genderDprimeEtaSq
```

### Criterion eta Squared
```{r echo=FALSE}
genderCriterionEtaSq
```



